An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-11-17 EconGrowth2.Rnw
Fixed functions to correctly handle energyType=NA.

Figure~\ref{fig:CD_Scatter_Graph} shows a ternary plot 
of $\alpha$, $\beta$, and $\gamma$ parameter values 
for resample models for the Cobb-Douglas model (without energy). 
In Figure~\ref{fig:CD_Scatter_Graph}, 
$\gamma$ is always 0.0, because energy is not included in this model.

<<CD_Scatter_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=ninePanelTernaryGraphHeight, fig.cap="Cobb-Douglas (without energy) resample model parameters.">>=
cdResampleTrianglePlot(energyType=NA)
@

>>>>

Figure~\ref{fig:CD_Scatter_Graph} shows a ternary plot 
of $\alpha$, $\beta$, and $\gamma$ parameter values 
for resample models for the Cobb-Douglas model (without energy).

<<CD_Scatter_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=ninePanelTernaryGraphHeight, fig.cap="Cobb-Douglas (without energy) resample model parameters. $\\gamma$ is always 0.0, because energy is not included in this model.">>=
cdResampleTrianglePlot(energyType=NA)
@
